\section{Results}
\label{results}
This section quantifies
the effects of~\acdc{} and determines if the performance of DCTCP
implemented in the vSwitch (\ie{}, \acdc{}) is equivalent to
the performance of DCTCP implemented in the host TCP stack.

\tightparagraph{Testbed}
The experiments are conducted on a physical testbed with 17 
IBM System x3620 M3 servers (6-core Intel Xeon
2.53GHz CPUs, 60GB memory) and Mellanox ConnectX-2 EN 10GbE NICs.
Our switches are IBM G8264, each with a buffer of 9MB shared
by forty-eight 10G ports. 
%The switches have dynamic memory management enabled by default.

\tightparagraph{System settings}
We run Linux kernel 3.18.0 which implements DCTCP as a 
pluggable module.
We set {{\tt $RTO_{min}$} to 10 ms~\cite{vasudevan2009safe,judd2015nsdi} and
set {\tt tcp\_no\_metrics\_save}, {\tt tcp\_sack} and {\tt tcp\_low\_latency} to 1.
\crs{Results are obtained with MTU sizes of 1.5KB and 9KB,
as networks typically use one of these settings. 
Due to space constraints, a subset of
the results are presented and unless otherwise noted, the MTU is set to 9KB.}



\tightparagraph{Experiment details}
To understand~\acdc{} performance, three different congestion control configurations
are considered. The baseline scheme, referred to as {\em CUBIC}, configures
the host TCP stack as CUBIC (Linux's default congestion control), which runs on top of an unmodified version of OVS.
Our goal is to be similar to {\em DCTCP}, which configures the host TCP
stack as DCTCP and runs on top of an unmodified version of OVS. Our scheme,{\em ~\acdc{}},
configures the host TCP stack as CUBIC (unless otherwise stated) and implements DCTCP congestion control in OVS.
In DCTCP and~\acdc{}, WRED/ECN is configured on the switches. In CUBIC,
WRED/ECN is not configured.

The metrics used are: TCP RTT (measured by sockperf~\cite{sockperf}),
TCP throughput (measured by iperf),
loss rate (by collecting switch counters) and
Jain's fairness index~\cite{jain-index}.
In \cref{macro}, flow completion time (FCT)~\cite{dukkipati2006flow} is used 
to quantify application performance.~\crs{All benchmark tools are run
in a container on each server, rather than in a VM.}

\input{microbenchmarks}
\input{macrobenchmarks}
