
Life is short, especially when you decide to pursue a PhD. How to
spend time wisely always puzzles me. Looking into the mirror, I am not
young anymore, but I feel very lucky for my stubborn decision and a
humble dream several years ago. Now, my school life almost ends. An
ending is also a new beginning. At this crossroad, let me thank those 
who have helped me both in work and life. 

% remzi and andrea
First, I would like to thank my advisors Remzi and Andrea
Arpaci-Dusseau. Before I worked with them, I was a frustrating
graduate student. They patiently helped me for many years to achieve
my research dream, including how to find a great 
problem, how to get inspiration, how to think deeply, how 
to communicate clearly, how to write a good paper, and how to do a
great presentation. I remember that they provided detailed suggestions
slide by slide in numerous late afternoon group meetings. I remember
many inspirational quotes from them: ``Double your reading sources'',
``Such is life'', ``We should target a best paper''. I remember that
they met me at Google Madison and Palo Alto downtown to listen to my
random ideas at random time. Remzi even taught me how to embed a joke
in my conference presentation. Doing research with them becomes easy,
fun and meaningful. 

I also learned a lot from their personalities. I was seriously sick
and rested at home for nearly one semester. I remember that Remzi
emailed me every Monday morning to ask what he can help. He offered to
talk to my doctor to make sure I was treated well. Remzi's great sense
of humor urged me to buy a book about how to have a sense of
humor. Andrea always smiles. She constantly encourages me and shares 
her confidence in my projects, especially during the hard time and the
deadline rush. They share their first-class OS book online for free,
making me rethink the value of money. Even though I decided to join
industry, they helped me greatly by connecting me with their friends
in many companies, and taught me how to negotiate offers wisely. What
else can you ask for? 

% thesis committee 
I would also like to thank my thesis committee. Shan Lu is also a
coauthor of my first paper here. I remember that she sat with me to
read many file system bug patches, and taught me different types of
concurrency bugs. She is willing to help when I need a recommendation
letter at various occasions. It is lucky to have Michael Swift as my
prelim and thesis committee. He is very rigorous and his extensive
questions, comments and feedback on different parts of my thesis
helped make it much better. I also thank Xinyu Zhang for reading my
thesis and giving me good suggestions. 

% internship mentors
I have been fortunate to do excellent internships throughout my PhD. 
I would like to thank the companies as well as my mentors there: 
Prasenjit Sarkar, Dinesh Subhraveti, Dean Hildebrand and Renu Tewari
at IBM; Herodotos Herodotou, Sriram Rao and Raghu Ramakrishnan at
Microsoft; Asit Desai and Sunil Satnur at VMWare. Working with these
people have been a great and rewarding experience for me. 

% colleagues
I am fortunate to work and discuss with a group of high quality
students here: Yupu Zhang, Thanumalayan Pillai, Thanh Do, Jun He,
Vijay Chidambaram, Yiying Zhang, Zev Weiss, Tyler Harter, Ao Ma,
Asim Kadav, Suli Yang, Chris Dragga, Leo Arulraj, Ramnatthan
Alagappan, Sriram Subramanian, and Swami Sundararaman. In particular,
I would like to thank my coauthors Yupu, Thanu and Thanh. Yupu is
always ready to discuss design and implementation details, help coding
and write the paper. Thanu's expertise in crash consistency and
hacking skills amazed me. Thanh gave me lots of great advice in
research and life. I also want to thank my officemate Vijay, who is
always full of motivation and curiosity. Having Thanu and Vijay as
officemates definitely helped me a lot to be a better researcher.  

% friends
I am grateful to have many friends at Madison to make my life more
interesting. I thank Ji Liu for being a great roommate when I arrived 
Madison. I thank the Shell Friday basketball team for numerous fun
games and great memories every Friday afternoon. I thank Wenbin Fang
and Jun He for inviting me to many delicious dinners at their homes. I 
thank Yvonne Koh for practicing English speaking with me patiently in
her free time. I also would like to thank many other friends at CS:
Jia Xu, Yinan Li, Linhai Song, Guoliang Jin, Wenfei Wu, Qian Wan,
Yimin Tan, Junming Xu, Yeye He, and Tan Zhang. With you all, the PhD
journey is not lonely anymore.   

% family
In closing, I turn towards family. I would like to thank my
parents for their unconditional love and support. They raised me in an
environment with an emphasis on education and good personality. They
set good examples for me in both work and life with their hard work 
and kindness. I have left home for study since I was 14. In these past
years, my parents always supported me to pursue my dreams, no matter how
far I will go and how long I will take. I remember that my mother
cried every time when I left home for high school, college and
graduate school. I remember my father woke me up and jogged with me
in the hills nearly every morning when I was home. Their love enables
me to go forward fearlessly. Finally, I thank my wife Xin for
her love since we met. She took care of me in many ways even though she is also
busy with her own research and study. I remember she cooked countless 
delicious meals for me when I work for various deadlines. She always
supports me, cheers me up and helps me to be a better person. I
dedicate this dissertation to my family: mother, father and Xin.  
