% The intro

Storage has becoming increasingly important to our modern world. 
Data is generated in an unprecedented speed, and new storage hardware
is also on the rise. Under this situation, various storage 
systems and applications have been developed to manage data more
reliably and efficiently. In this dissertation, we presented study
results that help us to understand the real problems in file systems
and proposed solutions that offer better reliability and performance
than existing file systems and key-value stores. 

We started by analyzing a large number of file system patches to
understand what are the real problems in modern file systems (\sref{chap-fs}).  
We focused on file system bugs, performance and reliability patches. 
We found that there are many bugs in both new and mature file systems,
and most of bugs may lead to serious consequences (data corruption or
system crashes). However, there is not enough isolation within a file
system to cope with corruption, crashes and performance problems. 
Therefore, we presented our solution IceFS, a new file system that
separates physical structures of the file system for better
reliability and performance isolation (\sref{chap-icefs}).  In
addition to file systems, we also found that physical entanglement of
keys and values in LSM-trees can lead to large I/O amplification and
disappointed performance in fast SSDs. We proposed WiscKey, a novel
LSM-tree based key-value store with a performance-oriented data layout
that separates keys and values to minimize I/O amplification(\sref{chap-wisckey}). 

In this chapter, we first summarize our contribution of this
dissertation (\sref{sec-conc-summary}). We then describe a set of  
general lessons we have learned in the course of this dissertation
work (\sref{sec-conc-lessons}). Finally, we discuss several possible
future research directions (\sref{sec-conc-future}). 

\input{conclusion/summary}
\input{conclusion/lessons}
\input{conclusion/future}
\input{conclusion/closing}
