\subsection{Delaying Durability}
\label{sec-related-durability}

The work of Nightingale \etal\ on ``rethinking the
sync''~\cite{Nightingale06-Rethink} has a similar flavor to OptFS. In
that work, the authors cleverly note that disk writes only need to
become durable when some external entity can observe said durability;
thus, by delaying persistence until such externalization occurs, huge
gains in performance can be realized. OptFS is complimentary, in that
it reduces the number of such durability events, instead enforcing a
weaker (and higher performance) ordering among writes, but avoiding
the complexity of implementing dependency tracking within the OS. In
cases where durability is required (\ie, applications use \sysdsync\
and not \syscsync), optimistic journaling does not provide much gain;
thus, Nightingale \etal's work still can be of benefit therein.

The work of Keeton \etal\ on disaster recovery argues that durability
can be traded for increased performance for many
applications~\cite{KeetonEtAl02-Designing}.
Snapmirror~\cite{patterson2002snapmirror}, Seneca~\cite{ji2003seneca},
and the Smoke and Mirrors File System
(SMFS)~\cite{weatherspoon2009smoke} are asynchronous (or
semi-synchronous) mirroring systems that trade off durability for
performance, similar to OptFS. All three systems use a modified form
of log-structured file systems~\cite{RosenblumOusterhout92-LFS} and
employ techniques similar to journaling. Using the terminology of
Seneca~\cite{ji2003seneca}, OptFS provides asynchronous out-of-order
atomic updates. The major difference between OptFS and these systems
is that OptFS can gain performance without any data loss. If we define
data loss as committed data that becomes unavailable, the performance
gain of OptFS comes from using \syscsync\ -- where users have no
expectations about the durability of data. In contrast, Snapmirror,
Seneca, and SMFS can lose committed data if there is a disaster.

% no osync - send barriers inserted
% assumed ordered transport protocol
% Snap mirror uses WAFL - very similar techniques to journaling
% no snapshots as in Seneca
% Talk about data loss - no data loss in OptFS!
% asynchronous out-of-order atomic update
